\Title

### 2021-05-28 latex/paper/main.tex
Began writing the proof of Theorem 10

%/========== Proof ==========/%
\section{Proof of Theorem \ref{thm:acrobot-energy-stabilization}}\label{sec:proof}
\textbf{TODO: prove Thm 10}

%/========== Conclusion ==========/%
\section{Conclusion}\label{sec:conclusion}

>>>>

%/========== Proof ==========/%
\section{Proof of Theorem \ref{thm:acrobot-energy-stabilization}}\label{sec:proof}
\textbf{TODO: prove Thm 10}
The sets \(\mathcal{O}_1\) and \(\mathcal{O}_2(\bar{\rho}\) are sublevel sets of
the nominal energy \(E(q_u,p_u)\) defined by \eqref{eqn:acrobot-energy}.
To prove Theorem \ref{thm:acrobot-energy-stabilization}, we will find conditions
under which the acrobot gains energy on an open ``energy annulus".
That is, given two energy levels \(E_0 \geq 0\) and \(E_1 > E_0\), we define the
energy annulus to be the domain
\[
    \mathcal{D} := \{(q_u,p_u) \in \SxR \mid \\
    E_0 < E(q_u,p_u) < E_1\}
    .
\]
The only condition we place on \(E_0\) and \(E_1\) is that they both correspond
to oscillations or both to rotations; that is, if \(E_0 < E(\pi,0)\), then 
\(E_1 \leq E(\pi,0)\).

Here is the fundamental idea of the proof: for certain open subsets
\(D \subset \mathcal{D}\), one can find a change of coordinates into 
pseudo-polar coordinates adapted to level sets of \(E\).
In other words, when \(I = 0\) in \eqref{eqn:acrobot-constraint}, one can find
a diffeomorphism \(T(q_u,p_u) = (r,\theta)\), where \(r\)
chooses a level set of \(E\) and \(\theta\) chooses a point on that level set.

We will describe the explicit forms of these transformations later. 
Thanks to the shape of a pendulum's orbits, we will show that (at \(I = 0\)) the
dynamics of \((r,\theta)\) satisfy \(\dot{r} = 0\) and \(\dot{\theta} > 0\).
By continuity of the constrained dynamics with respect to \(I\), we can find a
small enough \(I > 0\) so that \(\dot{\theta} > 0\) for the acrobot.
This property will enable us to perform a time-scaling transformation 
\(t = t(\theta)\) to eliminate the dynamics of \(\theta\), and study how 
the pseudo-radius \(r\) evolves as a function of the pseudo-angle \(\theta\),
rather than as a function of time.
If it increases ``on average" , then \(E\) must also be increasing ``on average"
and the constrained dynamics must be gaining energy on \(D\).

We formalize this idea in the following lemma.
Then we will find the relevant subset \(D \subset \mathcal{D}\)
and the coordinate transformations \((q_u,p_u) \mapsto (r,\theta)\) which
satisfy the conditions of the lemma, thereby proving the acrobot gains energy on
each set.

\begin{lemma}
    Consider the simplified acrobot \eqref{eqn:acrobot-hamiltonian} constrained
    by the VNHC \eqref{eqn:acrobot-constraint}, whose constrained dynamics are
    parameterized by \((q_u,p_u) \in \SxR\).
    Let \(D \subset \SxR\) be open and 
    let \(\underline{r}, \overline{r} \in \R_{> 0}\) with 
    \(\underline{r} < \overline{r}\).
    Suppose there exists a diffeomorphism 
    \begin{align*}
        T : D &\to ]\underline{r},\overline{r}[ \, \times \Sone \\
        (q_u,p_u) &\mapsto (r,\theta)
        ,
    \end{align*}
    satisfying \(\dot{r} = 0\) and \(\dot{\theta} > 0\) at \(I = 0\).
    Let \(g(\theta,r,I) = \dot{r}/\dot{\theta}\) and assume that 
    \((\partial g/\partial I)(\theta,r,0) = 0\).
    Define \(b(\theta,r_0) = g(\theta,r_0,0)\) and assume there exists
    \(\epsilon > 0\) such that 
    \[
        \int \limits_0^{2\pi} b(\sigma,r_0)d\sigma \geq \epsilon
        ,
    \]
    for all \(r_0 \in \, ]\underline{r},\overline{r}[\).
    Then there exists \(I^\star > 0\) small enough that the constrained dynamics
    gain energy on \(D\) for all \(0 < I \leq I^\star\), and lose energy on \(D\)
    for all \(-I^\star \leq I < 0\).
\end{lemma}
%/========== Conclusion ==========/%
\section{Conclusion}\label{sec:conclusion}
